Graphical representation example: Alternative interpretations

### 2023-11-24 notebooks/Graphical_representation_alternatives.Rmd
Computes the latent space grid (with detailed explanation)

We now compose the plot in the latent space. Apart from the item representation,
we need to plot the grid that corresponds to the latent space instead of the
test space.

@@

plot_oblique <- items_oblique |>
  arrange(desc(item))         |> # To plot them in reverse order
  ggplot(
    aes(
      origin_transf_1, origin_transf_2,
      xend  = end_transf_1, yend = end_transf_2,
      color = item, fill = item
    ),
  )                                                   +
  scale_x_continuous(
    limits       = c(-2, 3),
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  )                                                   +
  scale_y_continuous(
    limits       = c(-2, 2.8),
    breaks       = -3:3 * 2 * TAN_LS,
    labels       = function(y) 1 + y / (2 * TAN_LS),
    minor_breaks = 0,
    name         = NULL,
    oob          = oob_keep
  )                                                   +
  coord_fixed(expand = FALSE, clip = "on")            +
  scale_color_manual(values = PALETTE)                +
  geom_abline(slope = TAN_LS, linewidth = LINE_WIDTH) +
  geom_abline(
    slope     =  TAN_LS,
    intercept = -3:3 * 2 * TAN_LS,
    linewidth = LINE_WIDTH,
    linetype  = "17"
  )                                                         +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH)  +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  )                                                         +
  theme(
    axis.line          = element_blank(),
    panel.grid.major.x = element_line(
      color     = "black",
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```

@@

[^ls-coords]: This seems odd, there may be a mistake in the computation of the
latent space grid. Also, it seems like the coordinates are not correct, even if
they are (apparently) computed perpendicularly to the latent space axes.

>>>>

We now compose the plot in the latent space. Apart from the item representation,
we need to plot the grid that corresponds to the latent space instead of the
test space. I made a previous version of the grid, but then I realised that I
didn't quite understand how the grid should be built, apart from the axes.

Therefore, I decide to try to build it following this procedure:

1. First, I try to find the points where the two lines of the grid (one for each
axis) instersects in the coordinate "1" of the other axis.

2. Then I compute the transformed coordinates of point (1, 1).

3. Tracing a line from this point to each of the intersections of the two axes
gives the "base" grid lines. Then I only need to translate its coordinates by
an integer number to get any other grid line.

The points in step 1 must be the end of each of the two basis vectors.
Therefore, this step implies simply obtaining the coordinates of those basis
vectors in the orthonormal basis.

Then, step 2 is:

$$
\begin{pmatrix}
  1                          & 0 \\
  - \rho / \sqrt{1 - \rho^2} & 1 / \sqrt{1 - \rho^2}
\end{pmatrix}
\begin{pmatrix}
  1 \\ 1
\end{pmatrix} = 
\begin{pmatrix}
  1 \\ (1 - \rho) / \sqrt{1 - \rho^2}
\end{pmatrix}
$$

Finally, step 3:

- The first grid line through axis 2, in point/slope form:

$$
\begin{pmatrix}
  1 \\ (1 - \rho) / \sqrt{1 - \rho^2}
\end{pmatrix} -
\begin{pmatrix}
  0 \\ 1 / \sqrt{1 - \rho^2}
\end{pmatrix} =
\begin{pmatrix}
  1 \\ - \rho / \sqrt{1 - \rho^2}
\end{pmatrix}
$$

$$
slope = \frac{- \rho / \sqrt{1 - \rho^2}}{1} =
  - \frac{\rho}{\sqrt{1 - \rho^2}}
$$

$$
intercept = \frac{1}{\sqrt{1 - \rho^2}}
$$

- The first grid line through axis 1:

$$
\begin{pmatrix}
  1 \\ (1 - \rho) / \sqrt{1 - \rho^2}
\end{pmatrix} -
\begin{pmatrix}
  1 \\ - \rho / \sqrt{1 - \rho^2}
\end{pmatrix} =
\begin{pmatrix}
  0 \\ 1 / \sqrt{1 - \rho^2}
\end{pmatrix}
$$

It is thus a vertical line through (rectangular) coordinate
$(1, (1 - \rho) / \sqrt{1 - \rho^2})$.

@@

plot_oblique <- items_oblique |>
  arrange(desc(item))         |> # To plot them in reverse order
  ggplot(
    aes(
      origin_transf_1, origin_transf_2,
      xend  = end_transf_1, yend = end_transf_2,
      color = item, fill = item
    ),
  )                                                   +
  scale_x_continuous(
    limits       = c(-2, 3),
    breaks       = -2:3,
    # labels       = function(x) x * CORR_ARC_COSEC,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  )                                                   +
  scale_y_continuous(
    limits       = c(-2, 2.8),
    breaks       = -3:3 / CORR_ARC_SIN,
    labels       = function(y) y * CORR_ARC_SIN - 2 * CORR_VALUE,
    minor_breaks = 0,
    name         = NULL,
    oob          = oob_keep
  )                                                   +
  coord_fixed(expand = FALSE, clip = "on")            +
  scale_color_manual(values = PALETTE)                +
  geom_abline(slope = TAN_LS, linewidth = LINE_WIDTH) +
  geom_abline(
    slope     = TAN_LS,
    intercept = -3:3 / CORR_ARC_SIN,
    linewidth = LINE_WIDTH,
    linetype  = "17"
  )                                                         +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH)  +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  )                                                         +
  theme(
    axis.line          = element_blank(),
    panel.grid.major.x = element_line(
      color     = "black",
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```

@@

[^ls-coords]: This seems odd, there may be a mistake in the computation of the
latent space grid. Also, it seems like the coordinates are not correct, even if
they were computed perpendicularly to the latent space axes.
